---
title: "assignment 6"
author: "Soojung"
date: "3/14/2022"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Load Packages 
To start, load all the required packages with the following code. Install them if they are not installed yet.

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(knitr)
library(dplyr)
library(lubridate)
```



## Exercise 1. Tibble and Data Import
Import the data frames listed below into R and parse the columns appropriately when needed. Watch out for the formatting oddities of each dataset. Print the results directly, without using `kable()`.

You only need to finish any three out of the five questions in this exercise in order to get credit.

<br>

#### 1.1 Create the following tibble manually, first using `tribble()` and then using `tibble()`. Print both results. [We didn’t have time to cover this in class, but look up how these functions work here]

`tribble()`:

```{r}
tribble(
  ~a, ~b, ~b,
  #---|---|---
  1, 2.1, "apple",
  2, 3.2, "orange"
)
```

`tibble()`:

```{r}
tibble(
  a = 1:2, 
  b = c(2.1, 3.2), 
  c = c("apple", "orange")
)
```
#### 1.2 Import `https://raw.githubusercontent.com/nt246/NTRES-6100-data-science/master/datasets/dataset2.txt` into R. Change the column names into “Name”, “Weight”, “Price”.

```{r, warning = FALSE, message = FALSE, echo = T}
fruits <- read.delim("https://raw.githubusercontent.com/nt246/NTRES-6100-data-science/master/datasets/dataset2.txt", header=FALSE, sep=",")
names(fruits) = c("Name", "Weight", "Price")

fruits %>%
  as_tibble(fruits)%>%
  mutate(across(Weight, as.double))
```

#### 1.3 Import `https://raw.githubusercontent.com/nt246/NTRES-6100-data-science/master/datasets/dataset3.txt` into R. Watch out for the first few lines, missing values, separators, quotation marks, and deliminaters.

```{r}
fruits2 <- read.delim("https://raw.githubusercontent.com/nt246/NTRES-6100-data-science/master/datasets/dataset3.txt", skip = 3, header = FALSE, sep=";", na = c("?","Not Available"))

names(fruits2) = c("Name", "Weight", "Price")

fruits2 %>%
  mutate(across(Weight, as.double))%>%
  mutate_at("Name", str_replace_all, "/", "")%>%
  as_tibble(fruits2)
```

<br>

## Exercise 2. Weather Station
This dataset contains the weather and air quality data collected by a weather station in Taiwan. It was obtained from the Environmental Protection Administration, Executive Yuan, R.O.C. (Taiwan).

<br>

#### 2.1 Variable descriptions

* The text file `https://raw.githubusercontent.com/nt246/NTRES-6100-data-science/master/datasets/2015y_Weather_Station_notes.txt` contains descriptions of different variables collected by the station.

* Import it into R and print it in a table as shown below with kable().


```{r, echo = T}
data_para <- read.delim("https://raw.githubusercontent.com/nt246/NTRES-6100-data-science/master/datasets/2015y_Weather_Station_notes.txt", sep="-")
data_para %>%
  kable()
```

`#` indicates invalid value by equipment inspection 
`*` indicates invalid value by program inspection
`x` indicates invalid value by human inspection
`NR` indicates no rainfal
blank indicates no data

#### 2.2 Data tidying

* Import `https://raw.githubusercontent.com/nt246/NTRES-6100-data-science/master/datasets/2015y_Weather_Station.csv` into R. As you can see, this dataset is a classic example of untidy data: values of a variable (i.e. hour of the day) are stored as column names; variable names are stored in the `item` column.

* Clean this dataset up and restructure it into a tidy format.

* Parse the `date` variable into date format and parse `hour` into time.

* Turn all invalid values into `NA` and turn `NR` in rainfall into `0`.

* Parse all values into numbers.

* Show the first 6 rows and 10 columns of this cleaned dataset, as shown below, without using `kable()`.

*Hints: you don’t have to perform these tasks in the given order; also, warning messages are not necessarily signs of trouble.*


Before cleaning: 

```{r, warning = FALSE, message = FALSE, echo = T}
taiwan <- read.csv("https://raw.githubusercontent.com/nt246/NTRES-6100-data-science/master/datasets/2015y_Weather_Station.csv")

taiwan %>%
  as_tibble(taiwan)%>%
  select(1:10) %>%
  head(6)
```
After cleaning: 

```{r, warning = FALSE, message = FALSE, echo = T}
taiwan2 = taiwan %>%
  pivot_longer(c("X00":"X23"), names_to = "hour")%>%
  pivot_wider(names_from = item, values_from = value)%>%
  mutate_at("RAINFALL", str_replace_all, "NR", "0")%>%
  na_if("#")%>%
  na_if("*")%>%
  na_if("x")%>%
  mutate(date=parse_date(date))%>%
  mutate_at("hour", str_replace_all, "X", "")%>%
  mutate(hour=parse_time(hour, format="%h")) %>%
  mutate_at(c("AMB_TEMP", "CO", "NO", "NOx", "O3", "PM10", "PM2.5", "RAINFALL", "RH", "SO2", "WD_HR", "WIND_DIREC", "WIND_SPEED"), as.double)


taiwan2 %>%
  as_tibble(taiwan2)%>%
  select(1:10) %>%
  head(6)
```

#### 2.3 Using this cleaned dataset, plot the daily variation in ambient temperature on September 25, 2015, as shown below.


```{r, echo = T}
taiwan2 %>%
  filter(date == "2015-09-25") %>%
  ggplot(aes(x = hour, y = AMB_TEMP)) +
  geom_line()
```

#### 2.4 Plot the daily average ambient temperature throughout the year with a continuous line, as shown below.


```{r, warning = FALSE, message = FALSE, echo = T}
gg_base = taiwan2 %>%
  select(date, AMB_TEMP)%>%
  group_by(date) %>%
  summarise_at(vars(AMB_TEMP), funs(mean))%>%
  rename('daily_average_ambient_temp' = AMB_TEMP)

ggplot(data = gg_base, aes(x = date, y = daily_average_ambient_temp))+
  geom_line()
```

#### 2.5 Plot the total rainfall per month in a bar chart, as shown below.

*Hint: separating date into three columns might be helpful.*
```{r, echo = T}
gg_base2 = taiwan2 %>%
  mutate(month=format(date, "%m")) %>%
  group_by(month)%>%
  summarise_at(vars(RAINFALL), sum, na.rm = TRUE)%>%
  rename('MonthlyRainfall' = RAINFALL)%>%
  ggplot(aes(x = month, y = MonthlyRainfall)) +
  geom_col() 

gg_base2


```

#### 2.6 Plot the per hour variation in PM2.5 in the first week of September with a continuous line, as shown below.

*Hint: uniting the date and hour and parsing the new variable might be helpful.*

```{r, echo = T}
taiwan2 %>%
  filter(date >= "2015-09-01" & date <= "2015-09-08")%>%
  select(date, hour, PM2.5)%>%
  unite("time", date, hour) %>%
  mutate(time=parse_datetime(time, format = "%Y-%m-%d_%H:%M:%S"))%>%
  ggplot(aes(x = time, y = PM2.5))+
  geom_line()

```
